A title

### 2020-09-05 mstemc/post/technology/SignalsAndSystems/Chapter1BasicProblems3.tex
trivial commit

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
\definecolor{mycolor}{RGB}{139,0,0}
\author{Eason}
\date{\today}
\title{Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)},
 pdfkeywords={},
 pdfsubject={This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-21-0.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}

 \thispagestyle{empty}
 \begingroup
\begin{center}
 \vspace{\baselineskip}
 \textbf{\Huge Signals and Systems Chapter 1 Problems Part 3 (1.32-1.47)} \par
 \vspace{2\baselineskip}  \newline
 \textbf{\large Eason Zhang with www.makesteamclear.com \par}
 \vspace{\baselineskip} \newline
  \today \par
 \vspace{\baselineskip}
  \vfill
 \setlength{\unitlength}{3pt}
 \includegraphics[width=0.5\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-47d.pdf}
 \vfill \vspace{\baselineskip}
 \href{WWW.MAKESTEAMCLEAR.COM}{\Large WWW.MAKESTEAMCLEAR.COM} \par\newline
  makesteamclear is a free project, run by Eason Zhang, to make videos about STEAM in a more approachable way. If you find the contents in this article or the site or the youtube channel helpful, please consider \href{www.makesteamclear.com}{\ensuremath \heartsuit support me\ensuremath\heartsuit }, thanks \par
 \end{center}
 \endgroup

 \newpage \thispagestyle{empty} \textbf{copyright page} \newpage \tableofcontents \newpage
\hspace{0pt}\\

This post consists of solutions to problems from 1.21 to 1.31 in chapter 1 of the book Signals and Systems by Oppenheim ,Willsky and Nawab.\cite{oppenheim_signals_1997}

\section{Problem 1.32}
\label{sec:orgfc1022f}

@@

Let \(T\) be the fundamental period of \(y_{2}(t)\), then based on the analysis
of \hyperref[Problem 1.32c]{Problem 1.32c} , we have \(x(t)\) is a speeded up version of \(y_{2}(t)\),
hense \(x(t)\) is periodic and has fundamental period \(\frac{T}{2}\).
\section{Problem 1.33}
\label{sec:orgc6b726e}

@@

Based on the fact that only integer is valid for the independent variable of
discrete-time signal, \(y_{2}[n]\) contains all the value of \(x[n]\) at the
even index whereas at the odd index \(y_{2}[n]= 0\).
\section{Problem 1.34}
\label{sec:org4fc36d2}

@@

Notice that \(x_{e}(t)x_{o}(t)\) is and odd signal, so \(\int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt = 0\)
\section{Problem 1.35}
\label{sec:orgd2ae89c}

@@

When \(l = m/ \mathrm{gcd}(m,N)\), we have \(N_{0} = \frac{N}{ \mathrm{gcd}(m,N) }\).
\end{prf}
\section{Problem 1.36}
\label{sec:org4a7f30f}

@@

Based on the analysis of Problem 1.36a, we have fundamental period of \(x[n]\)
\begin{equation*}
N = m\frac{T_{0}}{T} = m \frac{q}{p}
\end{equation*}
Where \(m\) is the minimum integer so that \(N\) is an integer. Based on the
conclusion of \hyperref[sec:orgd2ae89c]{Problem 1.35} , we can re-express \(N\) as
\begin{equation*}
N = \frac{q}{\mathrm{gcd}(p,q)}
\end{equation*}
Where \(m = \frac{p}{\mathrm{gcd}(p,q)}\).
The fundamental frequency is
\begin{equation*}
\frac{2\pi}{N} = \frac{2\pi \mathrm{gcd}(p,q)}{q} = \omega_{0}T_{0} \frac{\mathrm{gcd}(p,q)}{q} = \omega_{0}T\frac{\mathrm{gcd}(p,q)}{p}
\end{equation*}

@@

Now, if we take the Nyquist's sampling into consideration, we must sampling a
baseband signal with at least two times higher frequency of the signal to
recover the baseband signal without alias. i.e. we must sample \(x(t) =
\cos(4\pi t)\) with a signal of fundamental frequency \(8\pi\) to get signal
\(x[n] = \cos(8\pi n)\).
\section{Problem 1.37}
\label{sec:org5b0c999}

@@

\begin{eqnarray*}
\phi_{yy}(t) &=& \int_{-\infty}^{+\infty} y(t+ \tau) y(\tau)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t+ \tau + T) x(\tau + T)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t + s) x(s) ds
\end{eqnarray*}
So we have \(\phi_{yy}(t) = \phi_{xx}(t)\).
\section{Problem 1.38}
\label{sec:orgef628d7}

@@

and \(u_{\Delta}^{6}(t)\) as :
\begin{equation*}
u_{\Delta}^{6}(t) =
\begin{cases}
\frac{1}{2} e^{\frac{t}{\Delta}} , & t< 0 \\
1 - \frac{1}{2}e^{ \frac{-t}{\Delta}} , & t> 0 \\
\end{cases}
\end{equation*}
So we can visualize them as below:
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38g.pdf}
\end{center}
\section{Problem 1.39}
\label{sec:org95fdb02}

@@

\end{equation*}
So \(g(t)\) has the same property as \(u(t)\)
\section{Problem 1.40}
\label{sec:org71282a6}

@@

We cannot reach that conclusion. Because for a system has memory, a certain
zero period \(t_{1}\) to \(t_{2}\) does not result the same zero period in the
output. Let's take \(y[n] = x[n-n_{0}]\) where \(n_{0}\neq 0\), the output will
have a delay ( \(n_{0}\) is positive) and an advance ( \(n_{0}\) is negative).
\section{Problem 1.41}
\label{sec:orgb5785da}

@@

Which means that the system is identical as the system in part (a) and hence the
system is time invariant.
\section{Problem 1.42}
\label{sec:org8f471d7}

@@

First we can express the interconnection of system 1 and system 2 as:
\begin{equation*}
y[n] =
\begin{cases}
x[ \frac{n}{2} ] + \frac{1}{4} x[ \frac{n-2}{2} ] , & n \ \mathrm{even} \\
\frac{1}{2} x[ \frac{n-1}{2} ] , & n \ \mathrm{odd}
\end{cases}
\end{equation*}
Then we express the interconnection of all the three systems.
\begin{equation*}
y[n] = x[ \tfrac{2n}{2} ] + \tfrac{1}{4} x[ \tfrac{2n-2}{2} ] = x[n] + \tfrac{1}{4} x[n-1]
\end{equation*}
So the system is an LTI system.
\section{Problem 1.43}
\label{sec:org772be8f}

@@

Suppose that we have a system:
\begin{equation*}
y[n] = 1
\end{equation*}
Then this system is time-invariant, any input will not change the property of
its output.
\section{Problem 1.44}
\label{sec:orgefef85f}

@@

\(m=1\) \(y[n] = x[n]\) is a linear system.
\(m=0\), \(y[n] = 1\) does satisfies that \(y[n]= 0, \forall n\)
\section{Problem 1.45}
\label{sec:orgb8bc776}

@@

The system is not causal because the output depends on all the value of \(x(t)\).
\section{Problem 1.46}
\label{sec:orgd263cd1}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-46b.pdf}
\end{center}
\section{Problem 1.47}
\label{sec:org09ffb49}

>>>>

% Intended LaTeX compiler: lualatex
\documentclass[koma,a4paper,utopia,12pt,listings-color,microtype,paralist,colorlinks,urlcolor=red]{org-article}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing,,backgrounds,positioning,fit,petri,calc,intersections,through,shapes.misc,mindmap,calendar,shadows,mindmap,calendar,graphdrawing,trees,shapes.misc,quotes,angles}
\definecolor{mycolor}{RGB}{139,0,0}
\author{Eason}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Eason},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

\section{Problem 1.32}
\label{sec:orgf15481f}

@@

Let \(T\) be the fundamental period of \(y_{2}(t)\), then based on the analysis
of \hyperref[Problem 1.32c]{Problem 1.32c} , we have \(x(t)\) is a speeded up version of \(y_{2}(t)\),
hense \(x(t)\) is periodic and has fundamental period \(\frac{T}{2}\).
\section{Problem 1.33}
\label{sec:orgf7b6502}

@@

Based on the fact that only integer is valid for the independent variable of
discrete-time signal, \(y_{2}[n]\) contains all the value of \(x[n]\) at the
even index whereas at the odd index \(y_{2}[n]= 0\).
\section{Problem 1.34}
\label{sec:orgb3a8c01}

@@

Notice that \(x_{e}(t)x_{o}(t)\) is and odd signal, so \(\int_{-\infty}^{+\infty} x_{e}(t)x_{o}(t) dt = 0\)
\section{Problem 1.35}
\label{sec:org1baca05}

@@

When \(l = m/ \mathrm{gcd}(m,N)\), we have \(N_{0} = \frac{N}{ \mathrm{gcd}(m,N) }\).
\end{prf}
\section{Problem 1.36}
\label{sec:org2d12240}

@@

Based on the analysis of Problem 1.36a, we have fundamental period of \(x[n]\)
\begin{equation*}
N = m\frac{T_{0}}{T} = m \frac{q}{p}
\end{equation*}
Where \(m\) is the minimum integer so that \(N\) is an integer. Based on the
conclusion of \hyperref[sec:org1baca05]{Problem 1.35} , we can re-express \(N\) as
\begin{equation*}
N = \frac{q}{\mathrm{gcd}(p,q)}
\end{equation*}
Where \(m = \frac{p}{\mathrm{gcd}(p,q)}\).
The fundamental frequency is
\begin{equation*}
\frac{2\pi}{N} = \frac{2\pi \mathrm{gcd}(p,q)}{q} = \omega_{0}T_{0} \frac{\mathrm{gcd}(p,q)}{q} = \omega_{0}T\frac{\mathrm{gcd}(p,q)}{p}
\end{equation*}

@@

Now, if we take the Nyquist's sampling into consideration, we must sampling a
baseband signal with at least two times higher frequency of the signal to
recover the baseband signal without alias. i.e. we must sample \(x(t) =
\cos(4\pi t)\) with a signal of fundamental frequency \(8\pi\) to get signal
\(x[n] = \cos(8\pi n)\).
\section{Problem 1.37}
\label{sec:org62dbfe6}

@@

\begin{eqnarray*}
\phi_{yy}(t) &=& \int_{-\infty}^{+\infty} y(t+ \tau) y(\tau)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t+ \tau + T) x(\tau + T)d\tau \\
&=& \int_{-\infty}^{+\infty} x(t + s) x(s) ds
\end{eqnarray*}
So we have \(\phi_{yy}(t) = \phi_{xx}(t)\).
\section{Problem 1.38}
\label{sec:org977ea11}

@@

and \(u_{\Delta}^{6}(t)\) as :
\begin{equation*}
u_{\Delta}^{6}(t) =
\begin{cases}
\frac{1}{2} e^{\frac{t}{\Delta}} , & t< 0 \\
1 - \frac{1}{2}e^{ \frac{-t}{\Delta}} , & t> 0 \\
\end{cases}
\end{equation*}
So we can visualize them as below:
\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-38g.pdf}
\end{center}
\section{Problem 1.39}
\label{sec:orgfa85644}

@@

\end{equation*}
So \(g(t)\) has the same property as \(u(t)\)
\section{Problem 1.40}
\label{sec:orge406af3}

@@

We cannot reach that conclusion. Because for a system has memory, a certain
zero period \(t_{1}\) to \(t_{2}\) does not result the same zero period in the
output. Let's take \(y[n] = x[n-n_{0}]\) where \(n_{0}\neq 0\), the output will
have a delay ( \(n_{0}\) is positive) and an advance ( \(n_{0}\) is negative).
\section{Problem 1.41}
\label{sec:org13d0b92}

@@

Which means that the system is identical as the system in part (a) and hence the
system is time invariant.
\section{Problem 1.42}
\label{sec:orgb6902d3}

@@

First we can express the interconnection of system 1 and system 2 as:
\begin{equation*}
y[n] =
\begin{cases}
x[ \frac{n}{2} ] + \frac{1}{4} x[ \frac{n-2}{2} ] , & n \ \mathrm{even} \\
\frac{1}{2} x[ \frac{n-1}{2} ] , & n \ \mathrm{odd}
\end{cases}
\end{equation*}
Then we express the interconnection of all the three systems.
\begin{equation*}
y[n] = x[ \tfrac{2n}{2} ] + \tfrac{1}{4} x[ \tfrac{2n-2}{2} ] = x[n] + \tfrac{1}{4} x[n-1]
\end{equation*}
So the system is an LTI system.
\section{Problem 1.43}
\label{sec:org51636a9}

@@

Suppose that we have a system:
\begin{equation*}
y[n] = 1
\end{equation*}
Then this system is time-invariant, any input will not change the property of
its output.
\section{Problem 1.44}
\label{sec:org159eee9}

@@

\(m=1\) \(y[n] = x[n]\) is a linear system.
\(m=0\), \(y[n] = 1\) does satisfies that \(y[n]= 0, \forall n\)
\section{Problem 1.45}
\label{sec:org4477d7c}

@@

The system is not causal because the output depends on all the value of \(x(t)\).
\section{Problem 1.46}
\label{sec:org34ba874}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{/Users/chaolongzhang/Dropbox/mstemc_hugo/static/img/tikz/figProb1-46b.pdf}
\end{center}
\section{Problem 1.47}
\label{sec:orgc922959}
